---
title: 'Bayesian inference for spatially-temporally misaligned data using predicive stacking'
subtitle: 'Supplementary code'
author: "Soumyakanti Pan, e-mail: span18@ucla.edu"
date: \today
output: 
  bookdown::html_document2:
    mathjax: "https://cdn.jsdelivr.net/npm/mathjax@3/es5/tex-mml-chtml.js"
    # self_contained: true
    theme: spacelab
    highlight: pygments
    toc: false
    number_sections: true
    df_print: kable
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment = NA, opts.label="kill_prefix", message = FALSE,
                      fig.align = 'center')
```

The following execution assumes installation of the R package **spStackCOS**, available for download and installation from the GitHub repository [SPan-18/spStackCOS-dev](https://github.com/SPan-18/spStackCOS-dev). If required, run the `run/installer.R` file to install all packages.

## Simulation
### Simulation of monthly aggregated ozone data

The following script simulates a monthly averaged exposure data at 50 locations in the unit square. The simulated data is plotted below.

```{r simData}
source("run/simData.R")
```

```{r plot1, echo=FALSE, fig.height=3.5, fig.width=12}
ggarrange(p1, p2.1, ncol = 2,
          labels = c("A", "B"), font.label = list(family = "sans"))
```

A: Simulated daily data is in *light blue*, and the monthly aggregated data is in *dark blue*; B: Interpolated spatial surface at a snapshot of the daily data.

### Fit a spatial-temporal regression model

We first load the `spStackCOS` package. Subsequently, we fit a spatial-temporal model on the simulated monthly average data, using monthly indicator basis function.

```{r fit1}
library(spStackCOS)
source("run/fit1_sptLMTimeAgg.R")
```

Posterior summary of coefficients of monthly indicators. Reference group: *January*.

```{r beta.CI}
library(kableExtra)
knitr::kable(t(apply(post_beta, 1, function(x) quantile(x, c(0.025, 0.5, 0.975))))) %>%
  kable_styling(full_width = FALSE)
```

## Posterior predictive inference

We seek both downscale and upscale posterior predictive inference at at arbitrary point locations in space and time, and at polygons and intervals.

#### Downscale prediction using monthly indicator basis

We perform downscale posterior predictive inference at a finer resolution - same set of locations, with each location predicted at 100 timestamps in the interval (0, 12).

```{r pred1}
source("run/pred1_sptPoint.R")
```

#### Downscale prediction using a periodic Fourier basis

For comparison, we fit a model with a mean function characterized by periodic Fourier bases, with periods 5, 6, 7, and 8. Subsequently, we do the same posterior predictive inference at the spatial-temporal locations as before.

```{r fit2}
source("run/fit2_sptLMTimeAgg.R")
source("run/pred2_sptPoint.R")
```

```{r plot2, echo=FALSE, fig.height=3.5, fig.width=12}
ggpubr::ggarrange(p3, p4, ncol = 2,
          labels = c("A", "B"), font.label = list(family = "sans"))
```

